Paper Figures

### 2019-09-18 PaperFigures.Rmd
took SEB phenotype out of main figs

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

#Figure 1 alt B

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

#Figure 1 alt C

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1C<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

@@

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, labels = c('C', 'D'), nrow=1, label_size = 20)
third_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('E'), label_size = 20)
figure2 = cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

@@

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, nrow=1, labels=c('B', 'C'), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, nrow=1, labels=c('D', 'E'), label_size = 20)
figure4 <- cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

@@

#Proliferation Assay
#Figure 6
##All Groups Responses to SEB
```{r}
og<-plot_filter(dplyr::filter(OG, Stim=="SEB"))
ogphen<-plot_filter(dplyr::filter(OGPHEN, Stim=="SEB"))

@@

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,5))
```

```{r, marker on proliferating, fig.width=15, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("CXCR3", "CCR4"))

sm<-allplot(melt, "TB", "value", all.cols)

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A', 'B'), nrow=1, label_size = 20, rel_widths = c(3,1))
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1,2,1), labels=c("C","D","E"), label_size = 20)
third_row= cowplot::plot_grid(tf, sm, labels=c('F', 'G'), nrow=1, label_size = 20)

figure6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3, rel_heights = c(1.5,2,2))
```

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-baseplot(melt, "TB", "value", ltbi.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    coord_cartesian(ylim=c(0,3))+
    labs(y="(%) Total CD4+ T cells")

@@

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c('E', 'F'), nrow=1, label_size = 20)
figure7<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3, rel_heights = c(2,2,2))
```

###On TH1 proliferating cells
```{r og th1 main four markers, fig.width=16, fig.height=8}
melt<-melt(ogth1, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

ogth1<-cowplot::plot_grid(a,b,ncol=2)
```

@@

cowplot::save_plot("figure1.png", figure1, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure1alt1.png", figure1B, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure1alt2.png", figure1C, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure2.png", figure2, base_height=14, base_width=16) #Figure 2
cowplot::save_plot("figure3.png", figure3, base_height=14, base_width=16)
cowplot::save_plot("figure4.png", figure4, base_height=14, base_width=12)
cowplot::save_plot("figure5.png", figure5, base_height=14, base_width=16)
cowplot::save_plot("figure6.png", figure6, base_height=16, base_width=16)
cowplot::save_plot("figure7.png", figure7, base_height=16, base_width=16)
cowplot::save_plot("figure8.png", lumplot, base_height=48, base_width=16)
```

@@

##Proliferation Supplementary
```{r}
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))
test$group<-"TH1/2"
for(i in 1:length(test$group)){
    if(test$variable[i] %in% c("T_G_x", "T_x_x", "x_G_x")){
        test$group[i]<- "TH1"
    }
    else if (test$variable[i] == "x_x_4"){
        test$group[i]<- "TH2"
    }
}

@@

supp6a<-booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    facet_grid(~group, scales="free_x", space="free_x")+
    labs(y="(%) Proliferating CD4+ T cells")

@@

supp6b<-booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Proliferating Mtb-Specific cells")
```

```{r}
supp6<-cowplot::plot_grid(supp6a, supp6b, nrow=2, labels=c("A", "B"), rel_widths = c(3,4))
```

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")
cowplot::save_plot("supp1.png", supp1, base_height=14, base_width=16)
cowplot::save_plot("supp2.png", supp2, base_height=28, base_width=16)
cowplot::save_plot("supp3.png", supp3, base_height=7, base_width=16)
cowplot::save_plot("supp4.png", supp4, base_height=14, base_width=16)
cowplot::save_plot("supp5.png", supp5, base_height=14, base_width=16)
cowplot::save_plot("supp6.png", supp6, base_height=14, base_width=16)
```

>>>>

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('B', 'C'), nrow=1, label_size = 20)
figure1<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

#Figure 1 alt B
```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

#Figure 1 alt C
```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('B', 'C'), nrow=1, label_size = 20)
figure1C<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

@@

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, labels = c('B', 'C'), nrow=1, label_size = 20)
third_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('D'), label_size = 20)
figure2 = cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

@@

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))+
    labs(y="")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, tf, sm, nrow=1, labels=c('B', 'C', 'D', 'E'), label_size = 20)
figure4opt1 <- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(3,4))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, nrow=1, labels=c('B', 'C'), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, nrow=1, labels=c('D', 'E'), label_size = 20)
figure4opt2 <- cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(2.5,4,4))

@@

#Proliferation Assay
#Figure 6
##All Groups Responses to SEB
```{r}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

og<-plot_filter(dplyr::filter(OG, Stim=="SEB"))
part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
seb<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4+ T cells",
         title="SEB")

og<-plot_filter(dplyr::filter(OG, Stim=="PEP", TB %in% c("LTBI", "TB")))
part2<-melt(og, id.vars=c("TB", "SM", "disease"), measure.vars="OG")
pep<-allplot(part2, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,3))+
    labs(title="CFP-10 & ESAT-6")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(seb, pep, nrow=1, rel_widths = c(3,2), labels=c("B", "C"), label_size = 20)
figure6<-cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1.5,3))

@@

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

@@

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, nrow=1, rel_widths = c(2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c('E', 'F'), nrow=1, label_size = 20)
figure7<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3, rel_heights = c(2,2,2))
```

@@

cowplot::save_plot("figure1.png", figure1, base_height=8, base_width=16) #Figure 1
#cowplot::save_plot("figure1alt1.png", figure1B, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure1alt2.png", figure1C, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure2.png", figure2, base_height=14, base_width=16) #Figure 2
cowplot::save_plot("figure3.png", figure3, base_height=14, base_width=16)

cowplot::save_plot("figure4-1.png", figure4opt1, base_height=10, base_width=16)
cowplot::save_plot("figure4-2.png", figure4opt2, base_height=15, base_width=14)

cowplot::save_plot("figure5.png", figure5, base_height=11, base_width=16)
cowplot::save_plot("figure6.png", figure6, base_height=10, base_width=12)
cowplot::save_plot("figure7.png", figure7, base_height=16, base_width=12)
cowplot::save_plot("figure8.png", lumplot, base_height=48, base_width=16)
```

@@

##Proliferation Supplementary
```{r}
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))

#cytokines
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))
two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,5))

#phenotypes
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))
tf<-allplot(melt, "TB", "value", all.cols)+    
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("CXCR3", "CCR4"))
sm<-allplot(melt, "TB", "value", all.cols)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20, rel_widths = c(3,1))
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1,2,1), labels=c("B","C","D"), label_size = 20)
third_row= cowplot::plot_grid(tf, sm, labels=c('F', 'G'), nrow=1, label_size = 20)

supp6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

```{r}
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))
test$group<-"TH1/2"
for(i in 1:length(test$group)){
    if(test$variable[i] %in% c("T_G_x", "T_x_x", "x_G_x")){
        test$group[i]<- "TH1"
    }
    else if (test$variable[i] == "x_x_4"){
        test$group[i]<- "TH2"
    }
}

@@

supp7a<-booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    facet_grid(~group, scales="free_x", space="free_x")+
    labs(y="(%) Proliferating CD4+ T cells")

@@

supp7b<-booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Proliferating Mtb-Specific cells")
```

```{r}
supp7<-cowplot::plot_grid(supp7a, supp7b, nrow=2, labels=c("A", "B"), rel_widths = c(3,4))
```

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")
cowplot::save_plot("supp1.png", supp1, base_height=14, base_width=16)
cowplot::save_plot("supp2.png", supp2, base_height=28, base_width=16)
cowplot::save_plot("supp3.png", supp3, base_height=7, base_width=16)
cowplot::save_plot("supp4.png", supp4, base_height=14, base_width=16)
cowplot::save_plot("supp5.png", supp5, base_height=14, base_width=16)
cowplot::save_plot("supp6.png", supp6, base_height=14, base_width=16)
cowplot::save_plot("supp7.png", supp6, base_height=14, base_width=16)
```
